---
execute: 
  echo: false
  output: true
  warning: false
format:
  html:
    theme: litera
    toc: true
    toc-location: left
    number-sections: false
    number-depth: 4
    highlight-style: espresso
    embed-resources: true
  docx: 
    toc: false
    reference-doc: "./docx/plos_one_theme.docx"
editor: visual
bibliography: "./bib/bibliography.bib"
link-citations: true
csl: "./csl/plos-one.csl"
---

```{r, include=FALSE}
#install packages helpful for hearing/audiology research 
if (!require(pacman)) install.packages('pacman')
pacman::p_load(tidyverse, patchwork, ggsci, ggpubr, reticulate)
```

```{r}
#load scripts 
source("scripts/scripts.R")
```

# **The title of the article (sentence case)**

**author one^1,4,⁎,¶^ , author two^2,¶^ , author three^3^**

^1^ Department, Institution, City, State, Country (no Zip code, abbreviations, and positon titles)

^2^ Department, Institution, City, State, Country (no Zip code, abbreviations, and positon titles)

^3^ Department, Institution, City, State, Country (no Zip code, abbreviations, and positon titles)

^4^ Department, Institution, City, State, Country (no Zip code, abbreviations, and positon titles)

^⁎^Corresponding author

Email: name\@domain.com (author name)

^¶^These authors contributed equally to this work.

# Abstract (Heading 1, sentence case)

Text

Text

Text

# Introduction

Text

Text

Example citation: A meta-analysis of studies surveying scientists about misconduct showed that \~2% of scientists admitted to having fabricated, falsified or modified data or results at least once, and up to \~34% admitted other questionable research practices [@fanelliHowManyScientists2009].

# Materials and Methods

Text

## Subsection (Heading 2, sentence case)

Text

### Subsection (Heading 3, sentence case)

Text

# Results

Cite figures as "Fig 1", "Fig 2", etc. in order.

Each figure caption should appear directly after the paragraph in which they are first cited.

Figure files should be saved as 'Fig1.tif', 'Fig1.tiff', or 'Fig1.eps' and uploaded separately as individual files.

```{r}
#when saving plots for publication, use the save_figure() function from the /scripts/scripts.R file. 
#the save_figure() function will save plots as .tiff format in the /figures folder
#example use: save_figure(plot = fig1, file_name = "Fig1")
```

**Fig 1. This is the Fig 1 Title.** Figure caption text here.

\[PLOS ONE guidelines for figures can be found [here](http://journals.plos.org/plosone/s/figures).\]

**Fig 2. This is the Fig 2 Title.** Figure caption text here.

**Table 1. This is the Table 1 Title.**

\[*Table goes here*\]

This is the Table 1 legend.

^a^Table footnotes belong here.

^b^Footnotes should have corresponding symbols in the table.

# Discussion

# Conclusions

# Acknowledgments

\[Acknowledgments go here\]

\newpage

# References

::: {#refs}
:::

\newpage

# Supporting information

::: supp
**S1 Fig. This is the S1 Fig Title.** This is the S1 Fig description.
:::

::: supp
**S2 Fig. This is the S2 Fig Title.** This is the S2 Fig description.
:::

::: supp
**S1 File. This is the S1 File Title.** This is the S1 File description.
:::

::: supp
**S1 Video. This is the S1 Video Title.** This is the S1 Video description.
:::

::: supp
**S1 Table. This is the S1 Table Title.** This is the S1 Table description.
:::
